landlord

### 2023-05-04 src/landlord.Rmd
create excel with landlord policies for each state

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)
library(ggplot2)

@@

# select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")
```

```{r}
#filter by new MSA list
# new_MSA_list <- unique(select_MSAs$cbsa)
# 
# MSA_landlord_data <- MSA_landlord_data %>% 
#   filter(cbsa %in% c(new_MSA_list))
```

@@

# #notice_of_entry_days
# MSA_landlord_data <- MSA_landlord_data %>% 
#   mutate(
#     notice_for_entry_days_num = case_when(
#       notice_for_entry_days == "N" ~ 1.0, 
#       notice_for_entry_days == "0" ~ 1.0,
#       notice_for_entry_days == "0.5" ~ 0.75,
#       notice_for_entry_days == "1" ~ 0.5,
#       notice_for_entry_days == "2" ~ 0.0,))
```

@@

datatable(MSA_landlord_data, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```

>>>>

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)
library(ggplot2)
library(readxl)
library(here)

@@

# for shiny app
state_deposit_data<- read_xlsx(here("data/raw/landlord_state_data.xlsx")) %>% clean_names()

eviction_notice <- read_xlsx(here("data/raw/landlord_state_data.xlsx"), sheet= "Sheet2") %>% 
  clean_names() %>% 
  rename(eviction_days = sel_min_nonpayment)

```{r wrangling state deposit limits}
# Define a regular expression pattern to match target phrases
phrase_pattern <- "(one|two)\\smonth|no\\sstatutory\\slimit"

# Define a function to extract matched words from each sentence
extract_words <- function(sentence, pattern) {
  words <- regmatches(sentence, gregexpr(pattern, sentence, ignore.case = TRUE))[[1]]
  if (length(words) > 0) {
    return(paste(words, collapse = " "))
  } else {
    return(NA)
  }
}

state_deposit_data$deposit_limit <- NA

# Create a new column with matched words
state_deposit_data <- state_deposit_data %>%
  mutate(matched_words = sapply(limit, extract_words, pattern = phrase_pattern))

# put matched words in new column
state_deposit_data$deposit_limit <- sapply(state_deposit_data$matched_words, extract_words, pattern = phrase_pattern)

# rename deposit data to apply weights
landlord_state_data <- state_deposit_data %>%
  mutate(deposit_limit = case_when(
    matched_words == "One month"   ~ "1_month_rent",
    matched_words == "Two month" ~ "2_months_rent",
    matched_words == "No statutory limit" ~ "N",
    TRUE ~ NA_character_
  )) %>% 
  select(state, limit, deposit_limit) %>% 
  inner_join(eviction_notice, by = join_by(state == jurisdictions))

#write result to google sheet
sheet_write(landlord_state_data, ss = "https://docs.google.com/spreadsheets/d/1A6o934oBp9Sdbxrx30GkVrGaX9PyzpS1pZc8Pz6Aoro/edit#gid=0", sheet = "MSA_landlord_data") # manually edited eviction data

# write output 
write.xlsx(landlord_state_data, here("data/intermediate/demographic.xlsx"), sheetName = "Sheet1")
```

@@

@@
